|

### 2022-07-24 manuscript.Rmd
linting + citation

```{r penguins-basic, echo=FALSE, fig.cap="Visualization showing the relationship between flipper length (mm) and bill length (mm) of penguins for three different species of penguins", fig.alt="", warning=FALSE, fig.height=3}
library(ggplot2) #It seems like the pkg chunk is not loading packages. I did not want to make changes there since I do not know what your intention was.
library(palmerpenguins)
fig <- ggplot(penguins, aes(flipper_length_mm, bill_length_mm, color = species)) +
         geom_point() +
  labs(x = "Flipper Length(mm)",
       y = "Bill Length (mm)",
       color = "Species") +
  theme_bw()

fig

```

The `colorblindr` package provides a set of functions that can be useful in teaching and practising color blindness accessibility. 
For instance, `cvd_grid()` function provides color-deficiency simulations of a given plot. 
In the code chunk below the plot is named as `fig`. 
The code creates a grid of four plots where each plot shows a different color vision deficiency.
This grid allows those without any color vision deficiencies experience what data visualizations would look like to a sighted person that does have color blindness.

>>>>

```{r penguins-basic, echo=FALSE, fig.cap="Visualization showing the relationship between flipper length (mm) and bill length (mm) of penguins for three different species of penguins", fig.alt="", warning=FALSE, fig.height=3}
library(ggplot2) # It seems like the pkg chunk is not loading packages. I did not want to make changes there since I do not know what your intention was.
library(palmerpenguins)
fig <- ggplot(penguins, aes(flipper_length_mm, bill_length_mm, color = species)) +
  geom_point() +
  labs(
    x = "Flipper Length(mm)",
    y = "Bill Length (mm)",
    color = "Species"
  ) +
  theme_bw()

fig
```

The `colorblindr` package [@R-colorblindr] provides a set of functions that can be useful in teaching and practising color blindness accessibility. 
For instance, `cvd_grid()` function provides color-deficiency simulations of a given plot. 
In the code chunk below the plot is named as `fig`. 
The code creates a grid of four plots where each plot shows a different color vision deficiency.
This grid allows those without any color vision deficiencies experience what data visualizations would look like to a sighted person that does have color blindness.
